The Cost of Undisturbed Landscapes

### 2020-04-28 projects/asparagus/doc/paper_clean.tex
postprocessing of asparagus results

% graphics
\usepackage{graphicx}

@@

    Due to the concentration of solar PV generation in time (both on a daily and on a seasonal scale), installing solar
    PV instead of wind power leads to an increase in dispatchable thermal generation.
    As thermal generation in Austria is predominantly by fossil thermal, this induces an increase in \COO emissions due
    to the increased use of PV.

@@

    \begin{figure*}
        \centering
        \includegraphics[width=0.8 \textwidth]{./figures/undisturbed_base.pdf}
        \caption{Opportunity cost of wind power assuming PV overnight cost of 630 EUR/kWp}
        \label{figure:opportunity-cost-base}
    \end{figure*}

>>>>

% graphics and figures
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

    Due to the concentration of solar PV generation in time (both on a daily and on a seasonal scale), installing solar
    PV instead of wind power leads to an increase in dispatchable thermal generation.
    As thermal generation in Austria is predominantly fossil thermal, this induces an increase in \COO emissions due
    to the increased use of PV\@.

    Curtailment in Austria is declining up to

@@

    \begin{figure*}
        \centering
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{./figures/undisturbed_base_share.pdf}
            \caption{Relative substitution}
            \label{fig:rel_substitution}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.475\textwidth}
            \centering
            \includegraphics[width=\textwidth]{./figures/undisturbed_base.pdf}
            \caption{Absolute substitution}
            \label{fig::abs_substitution}
        \end{subfigure}
        \caption{Opportunity cost of wind power assuming PV overnight cost of 630 EUR/kWp}
        \label{figure:opportunity-cost-base}
    \end{figure*}
